---
title: "Assignment 5 - Meta-analysis of pitch in schizophrenia"
author: "Riccardo Fusaroli"
date: "3/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Building on the shoulders of giants: meta-analysis

```{r}
# Load libraries
library(lmtest)
library(lme4)
library(lmerTest)
library(ggplot2)
library(dplyr)
library(MuMIn)
library(car)
library(plyr)
library(stringr)
library(tidyverse)
library(Metrics)
library(modelr)
library(caret)
library(cvTools)
library(simr)
library(MASS)
library(pastecs)
library(crqa)
library(nonlinearTseries)
library(pROC)
library(Scale)
library(pacman)
p_load(metafor)
```

```{r}
d = read.csv2("A5_Data.csv", stringsAsFactors = F)
```

## Questions to be answered

1. What is the current evidence for distinctive patterns of pitch mean and pitch sd in schizophrenia? Report how many papers report quantitative estimates, how many participants, your method to analyze them, the estimated effect size of the difference (mean effect size and standard error for pitch mean, same for pitch sd) and forest plots representing it. 

2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? Report the new estimates and the new forest plots. 
- standardize B, squared of random slope, paste in the data, save, reimport in R, rerun the analysis, see if it change anything

3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.


## Tips on the process to follow:

- Download the data on all published articles analyzing pitch in schizophrenia: https://www.dropbox.com/s/pmgw8wzc308so1p/Data.csv?dl=0
```{r}
# Rename Sample Size Controls coz there's a typo
d = rename(d, c(SampleSizeContros="SampleSizeControls"))

# Change fantors to numeric coz escalc has problems with factors
d$SampleSizeSchizo=as.numeric(d$SampleSizeSchizo)
d$SampleSizeControls=as.numeric(d$SampleSizeControls)
d$PitchMeanSchizo=as.numeric(d$PitchMeanSchizo)
d$PitchMeanControls=as.numeric(d$PitchMeanControls)
d$PitchSDSchizo=as.numeric(d$PitchSDSchizo)
d$PitchSDControls=as.numeric(d$PitchSDControls)
d$PitchMeanControlsSD=as.numeric(d$PitchMeanControlsSD)
d$PitchMeanSchizoSD=as.numeric(d$PitchMeanSchizoSD)
d$PitchSDSchizoSD=as.numeric(d$PitchSDSchizoSD)
d$PitchSDControlsSD=as.numeric(d$PitchSDSchizoSD)
```


- Following the procedure in the slides calculate effect size and standard error of the effect size per each study. N.B. we focus on pitch mean and pitch standard deviation.
```{r}
# Cohen's d = standardized effect size

# Pitch range for mean
PitchRangeMean = escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeControls, m1i=PitchMeanSchizo, m2i=PitchMeanControls, sd1i=PitchMeanSchizoSD, sd2i=PitchMeanControlsSD, data = d)

# Pitch range for SD
PitchRangeSD = escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeControls, m1i=PitchSDSchizo, m2i=PitchSDControls, sd1i=PitchSDSchizoSD, sd2i=PitchSDControlsSD, data = d)

```

```{r}
# Get number of participants included in the mean analysis
PitchRangeMean %>% 
  filter(is.na(yi)==F) %>%
  summarise(Schizo=sum(SampleSizeSchizo), Controls=sum(SampleSizeControls))

PitchRangeSD %>% 
  filter(is.na(yi)==F) %>%
  summarise(Schizo=sum(SampleSizeSchizo), Controls=sum(SampleSizeControls))
```

  - first try using lmer (to connect to what you know of mixed effects models)
```{r}
# lmer models
  # Mean
m1 = lmer(yi ~ 1 + (1|Article), weights = 1/vi,data = PitchRangeMean, control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"))
summary(m1)

  # SD
m2 = lmer(yi ~ 1 + (1|Article), weights = 1/vi,data = PitchRangeSD, control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"))
summary(m2)
```
 
  - then use rma() (to get some juicy additional statistics, and build a forest plot of the results (forest(model))
```{r}
# RMA
  # Mean 
rma_mean = res = rma(yi, vi, data = PitchRangeMean, slab=Article)
rma_mean 
forest(rma_mean , main = "Effect of mean")
  # SD
rma_sd = res = rma(yi, vi, data = PitchRangeSD, slab=Article)
rma_sd
forest(rma_sd, main = "Effect of SD")


# Tau^2 = overall variance
# I^2 = proportion of the variance due to heterogeneity (that cannot be reduced to within-study uncertainty)
```
 

- Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?
```{r}
# Read data
d2 = read.csv("../ExpM3-A3/final_rqa.csv")

# Chnge variables to factor
d2$participant=as.factor(d2$participant)
d2$study=as.factor(d2$study)

# Scale the data
d2 = d2 %>%
  dplyr::mutate_each_(funs(scale(.) %>%
                             as.vector),                           vars=c("mean","stdDev","range","median","InterquartileRange","MeanAbsoluteDeviation","coefficientOfVariation","delay","radius","embed","rqa_REC","rqa_DET","rqa_maxL","rqa_L","rqa_ENTR","rqa_TT","rqa_LAM"))
```

```{r}
# Get No. of participants, mean, sd 
SampleSizeSchizo = length(unique(d2$participant[d2$diagnosis == "schizophrenia"]))
SampleSizeControls = length(unique(d2$participant[d2$diagnosis == "control"]))
PitchMeanControls = mean(d2$mean[d2$diagnosis == "control"])
PitchMeanSchizo = mean(d2$mean[d2$diagnosis == "schizophrenia"])
PitchMeanControlsSD = sd(d2$mean[d2$diagnosis == "control"])
PitchMeanSchizoSD = sd(d2$mean[d2$diagnosis == "schizophrenia"])

PitchSDControls = mean(d2$stdDev[d2$diagnosis == "control"])
PitchSDSchizo = mean(d2$stdDev[d2$diagnosis == "schizophrenia"])
PitchSDControlsSD = sd(d2$stdDev[d2$diagnosis == "control"])
PitchSDSchizoSD = sd(d2$stdDev[d2$diagnosis == "schizophrenia"])
Article = "CogSci et al."
Year = 2017

# Create dataframe
schizo = data.frame(Article, Year, SampleSizeSchizo, SampleSizeControls, PitchMeanControls, PitchMeanControlsSD, PitchMeanSchizo, PitchMeanSchizoSD, PitchSDControls, PitchSDControlsSD, PitchSDSchizo, PitchSDSchizoSD)

# Merge with the rest of the dat
d_all = rbind(d,schizo)
```

```{r}
# Get effect size and sd for our study
  # Pitch range for mean
mean_all = escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeControls, m1i=PitchMeanSchizo, m2i=PitchMeanControls, sd1i=PitchMeanSchizoSD, sd2i=PitchMeanControlsSD, data = d_all)

  # Pitch range for SD
sd_all = escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeControls, m1i=PitchSDSchizo, m2i=PitchSDControls, sd1i=PitchSDSchizoSD, sd2i=PitchSDControlsSD, data = d_all)


# Get new number of participants
mean_all %>% 
  filter(is.na(yi)==F) %>%
  summarise(Schizo=sum(SampleSizeSchizo),Controls=sum(SampleSizeControls))

sd_all %>%
  filter(is.na(yi)==F) %>%
  summarise(Schizo=sum(SampleSizeSchizo),Controls=sum(SampleSizeControls))

```
- Now look at the output of rma() and check tau and I2
```{r}
# Now re-run the analysis
# lmer models
  # Mean
m3 = lmer(yi ~ 1 + (1|Article), weights = 1/vi,data = mean_all, control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"))
summary(m3)
  # SD
m4 = lmer(yi ~ 1 + (1|Article), weights = 1/vi,data = sd_all, control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"))
summary(m4)

# RMA
  # Mean 
rma_mean2 = res = rma(yi, vi, data = mean_all, slab=Article)
rma_mean2
forest(rma_mean2 , main = "Effect of mean")

  # SD
rma_sd2 = res = rma(yi, vi, data = sd_all, slab=Article)
rma_sd2
forest(rma_sd2, main = "Effect of SD")
```

```{r}
# Testing for influential studies
inf <- influence(rma_mean2)
print(inf)
plot(inf)

inf <- influence(rma_sd2)
print(inf)
plot(inf)
```

```{r}
# Funnel plots
funnel(rma_mean2, main = "Random-Effects Models of Effect of Mean",xlab = "Standardized Mean Difference") # looks fine
regtest(rma_mean2,digits= 3) # not significant
ranktest(rma_mean2,digits= 3) # not significant => no evidence for publication bias

funnel(rma_sd2, main = "Random-Effects Models of Effect of SD",xlab = "Standardized Mean Difference") # looks weird
regtest(rma_sd2,digits=3) # not significant
ranktest(rma_sd2)

# A significant rank correlation indicates a likely publication bias and inflated effect sizes due to small samples
```






