---
title: "Assignment 5 - Meta-analysis of pitch in schizophrenia"
author: "Riccardo Fusaroli"
date: "3/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Building on the shoulders of giants: meta-analysis
```{r}
p_load(metafor)
```

```{r}
# Load libraries
library(lmtest)
library(lme4)
library(lmerTest)
library(ggplot2)
library(dplyr)
library(MuMIn)
library(car)
library(plyr)
library(stringr)
library(tidyverse)
library(Metrics)
library(modelr)
library(caret)
library(cvTools)
library(simr)
library(MASS)
library(pastecs)
library(crqa)
library(nonlinearTseries)
library(pROC)
library(Scale)
library(pacman)
```

```{r}
d = read.csv2("A5_Data.csv", stringsAsFactors = F)
```

## Questions to be answered

1. What is the current evidence for distinctive patterns of pitch mean and pitch sd in schizophrenia? Report how many papers report quantitative estimates, how many participants, your method to analyze them, the estimated effect size of the difference (mean effect size and standard error for pitch mean, same for pitch sd) and forest plots representing it. 

2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? Report the new estimates and the new forest plots. 
- standardize B, squared of random slope, paste in the data, save, reimport in R, rerun the analysis, see if it change anything


3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.

## Tips on the process to follow:

- Download the data on all published articles analyzing pitch in schizophrenia: https://www.dropbox.com/s/pmgw8wzc308so1p/Data.csv?dl=0
```{r}
# Rename Sample Size Controls coz there's a typo
d = rename(d, c(SampleSizeContros="SampleSizeControls"))

# Change fantors to numeric coz escalc has problems with factors
d$SampleSizeSchizo=as.numeric(d$SampleSizeSchizo)
d$SampleSizeControls=as.numeric(d$SampleSizeControls)
d$PitchMeanSchizo=as.numeric(d$PitchMeanSchizo)
d$PitchMeanControls=as.numeric(d$PitchMeanControls)
d$PitchSDSchizo=as.numeric(d$PitchSDSchizo)
d$PitchSDControls=as.numeric(d$PitchSDControls)
d$PitchMeanControlsSD=as.numeric(d$PitchMeanControlsSD)
d$PitchMeanSchizoSD=as.numeric(d$PitchMeanSchizoSD)
d$PitchSDSchizoSD=as.numeric(d$PitchSDSchizoSD)
d$PitchSDControlsSD=as.numeric(d$PitchSDSchizoSD)
```

- Following the procedure in the slides calculate effect size and standard error of the effect size per each study. N.B. we focus on pitch mean and pitch standard deviation.
```{r}
# Pitch range for mean
PitchRangeMean = escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeControls, m1i=PitchMeanSchizo, m2i=PitchMeanControls, sd1i=PitchMeanSchizoSD, sd2i=PitchMeanControlsSD, data = d)

# Pitch range for SD
PitchRangeSD = escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeControls, m1i=PitchSDSchizo, m2i=PitchSDControls, sd1i=PitchSDSchizoSD, sd2i=PitchSDControlsSD, data = d)

```
 
  - first try using lmer (to connect to what you know of mixed effects models)
```{r}
# lmer models
  # Mean
m1 = lmer(yi ~ 1 + (1|Article), weights = 1/vi,data = PitchRangeMean, control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"))
summary(m1)

  # SD
m2 = lmer(yi ~ 1 + (1|Article), weights = 1/vi,data = PitchRangeSD, control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"))
summary(m2)
```
 
  - then use rma() (to get some juicy additional statistics, and build a forest plot of the results (forest(model))
```{r}
# RMA
  # Mean 
m3 = res = rma(yi, vi, data = PitchRangeMean, slab=Article)
forest(m3)
  # SD
m4 = res = rma(yi, vi, data = PitchRangeSD, slab=Article)
forest(m4)
```
 

- Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?
```{r}
# Read data
d2 = read.csv("../ExpM3-A3/final_rqa.csv")

# Chnge variables to factor
d2$participant=as.factor(d2$participant)
d2$study=as.factor(d2$study)

# Scale the data
d2 = d2 %>%
  dplyr::mutate_each_(funs(scale(.) %>%
                             as.vector),                           vars=c("mean","stdDev","range","median","InterquartileRange","MeanAbsoluteDeviation","coefficientOfVariation","delay","radius","embed","rqa_REC","rqa_DET","rqa_maxL","rqa_L","rqa_ENTR","rqa_TT","rqa_LAM"))
```


```{r}
# Model
m5 = glmer(stdDev ~ diagnosis + (1 + diagnosis|participant), d2) 
summary(m5)
```
```{r}
# Get the numbers we need
  # Yi = fixed effect, estimate = -0.05782
yi2 = fixed(m5)[(2)]
  #Vi = random effect, variance of participant =  0.2421
vi2 = random()



```



- Now look at the output of rma() and check tau and I2
